Location of crustacean Farms

### 2021-02-12 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
# mapview(coast_raw)
```

@@

For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
 - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
 - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
 - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province) or sub regional location. 
 - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 1.0)

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
names(farms_us_ne) <- c("lon", "lat") 
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 1.0)

@@

farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
names(farms_us_aqua) <- c("lon", "lat")
farms_us_aqua <- farms_us_aqua %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 1.0)

@@

farms_bal <- cbind(farms_bal, bal_subregions) %>%
  mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 1.0)

@@

farms_bal_area <- farms_bal_area %>%
  mutate(iso3c = "DNK") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 1.0)

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon)))
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 1.0)

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 1.0)

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Ireland" ~ "IRL",
    COUNTRY == "Bulgaria" ~ "BGR", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Netherlands" ~ "NLD",
    COUNTRY == "Italy" ~ "ITA", 
    COUNTRY == "Greece" ~ "GRC"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 1.0)

@@

farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014)) %>%
  mutate(iso3c = "ESP") %>%
  mutate(data_quality = 0.333)

@@

 - 5 licensed farms (only including "mollusc farm open")
 - Jersey Oyster Company Limited: 49.17300525845569, -2.0325974703629277
 - Seymour Oyster Company Ltd: 49.22644208989364, -2.0327040476242284
 - La Rocque Fisheries Limited: 49.17293132589725, -2.0312731919583795
 - Jersey Sea Farms: 49.231523271584344, -2.057638560247779
 - Island Dived Scallops: 49.20231914535721, -2.03533532472839

@@

farms_jey <- data.frame(lat = c(49.17300525845569, 49.22644208989364, 49.17293132589725, 49.231523271584344, 49.20231914535721),
                        lon = c(-2.0325974703629277, -2.0327040476242284, -2.0312731919583795, -2.057638560247779, -2.03533532472839)) %>%
  mutate(iso3c = "JEY") %>%
  mutate(data_quality = 1.0)

@@

buff <- st_buffer(g_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_ggy_final <- farms_ggy %>%
  mutate(iso3c = "GGY") %>%
  mutate(data_quality = 0.333)

@@

plot(slovenia_world_crop)
mapview(slovenia_world_crop)

@@

buff <- st_buffer(s_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_svn_final <- farms_svn %>%
  mutate(iso3c = "SVN") %>%
  mutate(data_quality = 0.333)

@@

buff <- st_buffer(c_meters, dist = 40000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_hrv_final <- farms_hrv %>%
  mutate(iso3c = "HRV") %>%
  mutate(data_quality = 0.333)

@@

Cayo Esquivel del Sur: 23.034188, -80.082047
Cayo de la Cruz: 22.994283, -79.994291
Cayo Hachuela: 22.952677, -79.963228
Cayos de la Enfermeria: 22.910246, -79.958924

@@

farms_cub <- data.frame(lat = c(23.0341889, 22.994283, 22.952677, 22.910246),
                        lon = c(-80.082047, -79.994291, -79.963228, -79.958924)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 0.667)

@@

farms_twn <- data.frame(lat = c(23.12185817551473),
                        lon = c(120.05482898155049)) %>%
  mutate(iso3c = "TWN") %>%
  mutate(data_quality = 0.0)

@@

```{r}
farms_pyf <- data.frame(lat = c(-17.349601342130857, -18.50754847683744),
                        lon = c(-138.40992718639146, -136.38467411084235)) %>%
  mutate(iso3c = "PYF") %>%
  mutate(data_quality = 1.0)

@@

buff <- st_buffer(k_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_ind_final <- farms_ind %>%
  mutate(iso3c = "IND") %>%
  mutate(data_quality = 0.333)

@@

farms_tha <- data.frame(do.call(rbind, st_geometry(tha_pts_latlon))) 
names(farms_tha) <- c("lon", "lat")
farms_tha <- farms_tha %>%
  mutate(iso3c = "THA") %>%
  mutate(data_quality = 0.667)

@@

```{r}
farms_idn <- data.frame(lat = c(3.2182751224662542, -5.964150035506321, -6.2646012824936275, -6.75680397048712, -6.975573928794459, -4.984732967006041, 0.889089620526810, -3.436748178542682, -5.142358892765042),
                        lon = c(99.69952320753342, 106.35924782378112, 108.0659620387556, 108.64496221771543, 112.61871244712762, 120.31326531641196, 123.52557614041675, 129.1920950239657, 137.4727448207172)) %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 0.667)

@@

farms_rus <- data.frame(lat = c(43.053493816917545),
                        lon = c(131.95698485517275)) %>%
  mutate(iso3c = "RUS") %>%
  mutate(data_quality = 0.0)

@@

buff <- st_buffer(nk_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_prk_final <- farms_prk %>%
  mutate(iso3c = "PRK") %>%
  mutate(data_quality = 0.333)

@@

sta_catarina_world_crop <- st_crop(coast_raw, sta_catarina_world_crs) %>% ## crop to santa catarina extent
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()

@@

buff <- st_buffer(sc_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 4) ## equally place the number of farms along the coastline 
class(sta_catarina_points_lines)
plot(sta_catarina_points_lines)

sta_catarina_points <- st_as_sf(sta_catarina_points_lines) %>%
  mutate(new_id = 1:28) %>%
  filter(new_id != 12)
mapview(sta_catarina_points)

@@

farms_bra_final <- farms_bra %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 0.333)

@@

# start with Capiz
capiz <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Capiz")
mapview(capiz)
plot(capiz)

@@

buff <- st_buffer(cp_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

# now do negros
negros <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Negros Occidental")
mapview(negros)

@@

buff <- st_buffer(n_meters, dist = 5000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

# now do samar 
samar <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Samar")
mapview(samar)

@@

# marabut to veriato

@@

buff <- st_buffer(sm_meters, dist = 3000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 0.333)

@@

farms_mys <- data.frame(lat = c(4.074359958576369),
                        lon = c(100.73343376478226)) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 0.0)

@@

farms_khm <- data.frame(lat = c(11.069927194335508),
                        lon = c(103.64594001534627)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 0.0)

@@

farms_hkg <- data.frame(lat = c(22.48384043911231),
                        lon = c(113.98143449612208)) %>%
  mutate(iso3c = "HKG") %>%
  mutate(data_quality = 0.667)

@@

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality)

>>>>

coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")

@@

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
names(farms_us_ne) <- c("lon", "lat") 
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 5.0) %>%
  mutate(action_needed = "Land mask")

@@

farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
names(farms_us_aqua) <- c("lon", "lat")
farms_us_aqua <- farms_us_aqua %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_bal <- cbind(farms_bal, bal_subregions) %>%
  mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_bal_area <- farms_bal_area %>%
  mutate(iso3c = "DNK") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon)))
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Ireland" ~ "IRL",
    COUNTRY == "Bulgaria" ~ "BGR", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Netherlands" ~ "NLD",
    COUNTRY == "Italy" ~ "ITA", 
    COUNTRY == "Greece" ~ "GRC"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014)) %>%
  mutate(iso3c = "ESP") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

 - 5 licensed farms (only including "mollusc farm open"): Locations estimated from maps and addresses listed 
 - Jersey Oyster Company Limited: 49.172680993306905, -2.0255193115109957
 - Seymour Oyster Company Ltd: 49.220095937386375, -2.0215887506551438
 - La Rocque Fisheries Limited: 49.169912669200976, -2.0230904378277916
 - Jersey Sea Farms: 49.242435452408536, -2.060618920921559
 - Island Dived Scallops: 49.20656011166959, -2.0158403231425996

@@

farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
                        lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
  mutate(iso3c = "JEY") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

buff <- st_buffer(g_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_ggy_final <- farms_ggy %>%
  mutate(iso3c = "GGY") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

mapview(slovenia_world_crop)

@@

buff <- st_buffer(s_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_svn_final <- farms_svn %>%
  mutate(iso3c = "SVN") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

buff <- st_buffer(c_meters, dist = 40000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_hrv_final <- farms_hrv %>%
  mutate(iso3c = "HRV") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

Cayo Esquivel del Sur: 23.034188, -80.082047
Cayo de la Cruz: 22.994283, -79.994291
Cayo Hachuela: 22.952677, -79.963228
Cayos de la Enfermeria: 22.90988409545137, -79.94865189587235

@@

farms_cub <- data.frame(lat = c(23.0341889, 22.994283, 22.952677, 22.90988409545137),
                        lon = c(-80.082047, -79.994291, -79.963228, -79.94865189587235)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_twn <- data.frame(lat = c(23.12185817551473),
                        lon = c(120.05482898155049)) %>%
  mutate(iso3c = "TWN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

```{r}
farms_pyf <- data.frame(lat = c(-17.349601342130857, -18.50754847683744),
                        lon = c(-138.40992718639146, -136.38467411084235)) %>%
  mutate(iso3c = "PYF") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

buff <- st_buffer(k_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_ind_final <- farms_ind %>%
  mutate(iso3c = "IND") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

farms_tha <- data.frame(do.call(rbind, st_geometry(tha_pts_latlon))) 
names(farms_tha) <- c("lon", "lat")
farms_tha <- farms_tha %>%
  mutate(iso3c = "THA") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

```{r}
farms_idn <- data.frame(lat = c(3.2182751224662542, -5.964150035506321, -6.2646012824936275, -6.75680397048712, -6.975573928794459, -4.984732967006041, 0.889089620526810, -3.436748178542682, -5.142358892765042),
                        lon = c(99.69952320753342, 106.35924782378112, 108.0659620387556, 108.64496221771543, 112.61871244712762, 120.31326531641196, 123.52557614041675, 129.1920950239657, 137.4727448207172)) %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_rus <- data.frame(lat = c(43.053493816917545),
                        lon = c(131.95698485517275)) %>%
  mutate(iso3c = "RUS") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

buff <- st_buffer(nk_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

farms_prk_final <- farms_prk %>%
  mutate(iso3c = "PRK") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

sta_catarina_world_crop <- st_crop(coast_raw, sta_catarina_world_crs) %>% ## crop to santa catarina extent
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>% ## union all the geometries
  ungroup()

@@

buff <- st_buffer(sc_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

@@

sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 24) ## equally place the number of farms along the coastline 
class(sta_catarina_points_lines)
plot(sta_catarina_points_lines)

sta_catarina_points <- st_as_sf(sta_catarina_points_lines) %>%
  mutate(new_id = 1:168)  %>%
  filter(new_id %in% c(1:24, 158, 64, 78))

mapview(sta_catarina_points)

@@

farms_bra_final <- farms_bra %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

# start with Capiz by placing 300 points along the coast 
capiz <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Capiz")
mapview(capiz)
plot(capiz)

@@

buff <- st_buffer(cp_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

# now lets place 10 points along the coast of Negros Occidental 
negros <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Negros Occidental")
mapview(negros)

@@

buff <- st_buffer(n_meters, dist = 5000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

# now lets place 250 points along the coast of samar 
samar <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Samar")
mapview(samar)

@@

@@

buff <- st_buffer(sm_meters, dist = 3000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

farms_mys <- data.frame(lat = c(4.074359958576369),
                        lon = c(100.73343376478226)) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

farms_khm <- data.frame(lat = c(11.069927194335508),
                        lon = c(103.64594001534627)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

farms_hkg <- data.frame(lat = c(22.48384043911231),
                        lon = c(113.98143449612208)) %>%
  mutate(iso3c = "HKG") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality, -action_needed)

### 2021-02-12 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

Now we will map crustacean farms. Workflow will be as follows:

 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of crustacean farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
 - Lastly, if there is no evidence of marine crustacean farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

@@

farms_idn <- data.frame(lat = c(0.3359943014669836),
                        lon = c(117.55582991782983)) %>%
  mutate(iso3c = "IDN")

@@

farms_chn <- data.frame(lat = c(29.378009267567716),
                        lon = c(121.95043909100868)) %>%
  mutate(iso3c = "CHN")

@@

farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325919306644522),
                        lon = c(89.49499697244659, 91.76441856678511)) %>%
  mutate(iso3c = "BGD")

@@

farms_mmr <- data.frame(lat = c(15.930407995930784, 18.615093163569437),
                        lon = c(94.76647475697742, 94.24290607527016)) %>%
  mutate(iso3c = "MMR")

@@

farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055231),
                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.789267),
                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
  mutate(iso3c = "VNM")

@@

phl_lat_lon <- phl_mudcrab_prod %>%
  left_join(provinces, by = "Province") %>%
  dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
  mutate(iso3c = "PHL")

@@

write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)

>>>>

Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

farms_idn <- data.frame(lat = c(0.3359943014669836),
                        lon = c(117.55582991782983)) %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

farms_chn <- data.frame(lat = c(29.378009267567716),
                        lon = c(121.95043909100868)) %>%
  mutate(iso3c = "CHN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325670145257305),
                        lon = c(89.49499697244659, 91.76091935028879)) %>%
  mutate(iso3c = "BGD") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_mmr <- data.frame(lat = c(15.930407995930784, 18.615093163569437),
                        lon = c(94.76647475697742, 94.24290607527016)) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055819944690162),
                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.79073953273914),
                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
  mutate(iso3c = "VNM") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

phl_lat_lon <- phl_mudcrab_prod %>%
  left_join(provinces, by = "Province") %>%
  dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv"), row.names = FALSE)

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality, -action_needed)

write.csv(all_farms_1, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
```
